DATA 621 Homework #3

### 2019-10-31 DATA621/HW3.Rmd
Finalize HW3

@@

### Splitting the Data
Next, we look to split our data between a training set (`train`) and a test data set (`test`). We'll use a 70-30 split between train and test, respectively.
```{r}
set.seed(42)
train_index <- createDataPartition(df$target, p = .7, list = FALSE, times = 1)
train <- df[train_index,]
test <- df[-train_index,]
```

### Exploratory Data Analysis
Now, let's look at our training data. By looking at a correlation matrix, we can see which variables may be too correlated to be included together in a model as predictor variables. This will help us later during the model selection process.

@@

>>>>

## Introduction

We have been given a dataset with `r nrow(df)` records summarizing a attributes of various neighborhoods of a major city.  Each record in the training dataset has a response variable that is 1 when the neighborhood's crime rate is above the median and 0 when it is not.  In all there are `r ncol(df)-1` predictors.  We will construct a logistic regression model to predict the classification of the evaluation data set.

@@

### Splitting the Data

Next, we look to split our data between a training set (`train`) and a test data set (`test`). We'll use a 70-30 split between train and test, respectively.
```{r}
set.seed(42)
train_index <- createDataPartition(df$target, p = .7, list = FALSE, times = 1)
train <- df[train_index,]
test <- df[-train_index,]
```

### Exploratory Data Analysis

Now, let's look at our training data. The following table summarizes the predictor variables of the training set:

```{r}
train %>%
  select(-target) %>%
  summary() %>%
  kable() %>%
  kable_styling()
```

By looking at a correlation matrix, we can see which variables may be too correlated to be included together in a model as predictor variables. This will help us later during the model selection process.

@@

## Final Selection and Predictions

Having looked at the F1 statistics and the ROC curves we will use the model1 to form our final predictions.

```{r}
evaluation$target <- ifelse(predict.glm(model1, evaluation, "response") < 0.5, 0, 1)
evaluation %>%
  write.csv(., "./data/hw3-predictions.csv", row.names = F)
```
